\documentclass[letterpaper, nocolor, draft]{moderncv}
\moderncvtheme{classic}
\usepackage[scale=0.75]{geometry}
\recomputelengths
\moderncvcolor{blue}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\nopagenumbers{}

\firstname{AliSina}
\familyname{Karimi}

% \title{Software Developer}

\email{alisinakarimi.2003@gmail.com}
 \homepage{alisinadevelo.github.io}
% \extrainfo{}
% \photo[][]{}
\social[github]{AliSinaDevelo}
\social[linkedin]{alisina-karimi-43a834224}

% \renewcommand{\section}[1]{\vspace{6pt}\par{\large\textbf{#1}}\par\nobreak\vspace{4pt}\hrule\vspace{8pt}}


\begin{document}
\title{Software Engineer}
\maketitle

\section{Summary}
Aspiring computer scientist and versatile software engineer driven by a deep-seated curiosity for advancing technology. Dedicated to pioneering innovative solutions through comprehensive knowledge of programming languages and frameworks. With a solid foundation in software development principles and a keen interest in research, I strive to push the boundaries of possibility in the digital realm. Eager to contribute my skills and passion for discovery to challenging projects and collaborative environments, shaping the future of computing.

\section{Education}
\cventry{September 2021 - 2025}{Polytechnic of Turin} {Bachelor of Science - Computer Engineering}{
Greater Turin Metropolitan Area, Piedmont, Italy}{}{Relevant coursework:   }

\section{Experience}
\cventry{September 2022 - May 2024}{Member, Developer in AreaIT}{RUN Polito APS-ETS}{Greater Turin Metropolitan Area, Piedmont, Italy}{}{
\begin{itemize}
\item Contributes as a member to the development of the RUN Polito APS-ETS internal framework.
\item Engaged in programming tasks within the project's web stack using  JavaScript, Go, and other relevant technologies
\end{itemize}
}

\cventry{May 2022 - August 2022}{Back-end Developer}{WEEEOpen}{Greater Turin Metropolitan Area, Piedmont, Italy}{}{
\begin{itemize}
\item Assisted senior developers with the design, development, and testing of web applications using React, Django, and Node.js
\item Collaborated with cross-functional teams to identify and solve technical issues and improve the user experience of web applications
\item Contributed to the development of internal tools and automation scripts to streamline software development processes
\end{itemize}
}

\section{Skills}
\cvitem{Languages}{C, Go, Python, JavaScript/TypeScript, Bash, SQL}
\cvitem{Web Technologies}{HTML, CSS, Bootstrap, Tailwind CSS}
\cvitem{Containeri-\\zation tools}{Docker, Kubernetes}
\cvitem{Code Editors}{Emacs}
\cvitem{Cloud Platforms}{AWS, Firebase}
\cvitem{Databases}{MySQL, PostgreSQL, SQLite,  MongoDB}
\cvitem{Frameworks}{Vue.js, Node.js, React, Django, Svelte, FastAPI}
%\cvitem{}

\section{Projects}

\subsection{Chatster}

\cvlistitem{Designed and developed using Go for backend infrastructure management.}
\cvlistitem{Utilized ReactJS for frontend development.}
\cvlistitem{Chatster is a comprehensive real-time chat application equipped with a wide array of features. It serves as a robust framework adaptable for various chat systems within organizational environments.}

\subsection{Newsact}

\cvlistitem{Developed using Python in conjunction with Scikit-learn.}
\cvlistitem{Newsact functions as a machine learning tool engineered to discern between authentic news and misinformation, thus combating the proliferation of fake news.}

\subsection{Quorabust}

\cvlistitem{Implemented using Python, employing Bag-of-Words (BOW), TFIDF, and XGBoost algorithms.}
\cvlistitem{Quorabust serves as a tool facilitating the discovery of similar Quora questions to aid users in finding pertinent answers. Its functionality aims to streamline the process of locating relevant information within the Quora platform.}

\section{Certifications}
% \cventry{}{Algorithms Specialization}{Stanford University}{}{}{}
%\cventry{}{Machine Learning Specialization}{Stanford University x DeepLearning.AI}{}{}{}
\cventry{}{Python for Everybody}{University of Michigan - Ann Arbor}{}{}{}
\cventry{}{Meta Front-End Developer Professional Certificate}{Meta}{}{}{}
\cventry{}{Meta Back-End Developer Professional Certificate}{Meta}{}{}{}
\cventry{}{Full-Stack Legacy Certification}{FreeCodeCamp}{}{}{}

\section{Languages}
\cvlanguage{English}{Native or Bilingual Proficiency}{}
\cvlanguage{Persian}{Native or Bilingual Proficiency}{}
\cvlanguage{German}{Full Professional Fluency}{}
\cvlanguage{Italian}{Fluent}{}
\cvlanguage{French}{Fluent}{}

\end{document}